Redundant calibration as a complex optimization problem

### 2017-01-04 paper.tex
added symbol for modified hessian

\newcommand{\bz}{\bmath{z}}
\newcommand{\bs}{\bmath{s}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\bB}{\bmath{B}}
\newcommand{\bC}{\bmath{C}}
\newcommand{\bE}{\bmath{E}}
\newcommand{\bF}{\bmath{F}}
\newcommand{\bG}{\bmath{G}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bH}{\bmath{H}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\bO}{\bmath{O}}
\newcommand{\bP}{\bmath{P}}
\newcommand{\bQ}{\bmath{Q}}
\newcommand{\bR}{\bmath{R}}
\newcommand{\bI}{\bmath{I}}
\newcommand{\ba}{\bmath{a}}
\newcommand{\bb}{\bmath{b}}
\newcommand{\bx}{\bmath{x}}
\newcommand{\bp}{\bmath{p}}
\newcommand{\bmJ}{\bmath{\mathcal{J}}}
\newcommand{\bzero}{\bmath{0}}
%\newcommand{\bvarrho}{\bmath{\varrho}}
%\newcommand{\bnu}{\bmath{\nu}}
%\newcommand{\bvarphi}{\bmath{\varphi}}
\newcommand{\conj}[1]{\overline{#1}}

@@

\section{Conjugate Gradient Method}
The Conjugate Gradient (CG) method was independently discovered by \citet{Hestenes1973} and \citet{Stiefel1952}. They later published a joint paper, which is now considered as the seminal
reference on CG \citep{Hestenes1952}. The iterative CG method is used to solve a particular class of linear system. The CG method is generally used to solve
\begin{equation}
\label{eq:linear_system}
\bb = \bA\bx,
\end{equation}
where $\bb\in\mathbb{C}^P$ is a known complex column vector of size $P$, $\bx\in\mathbb{C}^P$ is an unknown complex column vector with the same length as $\bb$, and $\bA\in\mathbb{C}^{P\times P}$ is a square positive-definite Hermitian matrix with the appropriate dimensions.  
Moreover, using the CG method to solve Eq.~\eqref{eq:linear_system} will only be computationally advantageous if $\bA$ is also sparse (contain many zero entries).
Using the iterative CG method to solve large sparse linear sytems was popularized by \citet{Reid1971}. A good tutorial on the CG method can be found in \citep{Shewchuk1994}.
The iterative CG method is presented in Algorithm \ref{algo:CG}.

@@

\subsection{Normal Equation}
Lets assume that instead of Eq.~\eqref{eq:linear_system} we have a more general linear system, i.e.
\begin{equation}
 \bb = \bB\bx,
\end{equation}
where $\bb\in\mathbb{C}^K$, $\bx\in\mathbb{C}^P$  and $\bB\in\mathbb{C}^{K \times P}$, with $K > P$. We can use the normal equation 
\begin{equation}
\label{eq:normal_equation}
\bB^H\bB\bx = \bB^H\bb 
\end{equation}
to estimate the $\bx$ that minimizes
\begin{equation}
\label{eq:norm_ls}
\|\bb-\bB\bx\|_F^2. 
\end{equation}
There are a few important observations that we can make while inspecting Eq.~\eqref{eq:normal_equation}:
\begin{enumerate}
\item $\bB^H\bB$ is a square positive semi-definite Hermitian matrix by construction.
\item $\bB^H\bb$ is in the column range of $\bB^H\bB$; this follows trivially from 
\begin{equation}
\bB^H\bb \in \mathcal{R}(\bB^H) \implies \bB^H\bb \in \mathcal{R}(\bB^H\bB).   
\end{equation}
\end{enumerate}

@@

\subsubsection{Complex GN and LM}
In this section we discuss how we can use the GN and LM algorithms to solve Eq.~\eqref{eq:least_squares_complex} (i.e. estimate $\breve{\bz}$). The complex Jacobian is defined to be
\begin{equation}
\label{eq:Jacobian}
\bJ = \begin{bmatrix}
       \bmJ & \bmJ^*\\
       \conj{\bmJ}^* & \conj{\bmJ} 
      \end{bmatrix},
\end{equation}
where 
\begin{align}
\bmJ &= \frac{\partial \bv}{\partial \bz}, & \bmJ^* &= \frac{\partial \bv}{\partial \conj{\bz}}. 
\end{align}
In Eq.~\eqref{eq:Jacobian}, $\frac{\partial}{\partial \bz}$ and $\frac{\partial}{\partial \conj{\bz}}$ respectively denote the cogradient operator and the conjugate cogradient operator \citep{Sorber2012}.
The GN update step is now defined as:
\begin{equation}
\label{eq:GN_update}
 \Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\br}.
\end{equation}
The LM update rule is very similar, the major difference being a damping factor $\lambda_{\textrm{LM}}$ is introduced:
\begin{equation}
\label{eq:LM_update}
\Delta \breve{\bz} = (\bJ^H\bJ + \lambda_{\textrm{LM}}\bD)^{-1}\bJ^H\breve{\br},
\end{equation}
where $\bD=\bI\odot\bJ^H\bJ$.

@@

Replacing $\breve{\br}$ with $\breve{\bd}-\breve{\bv}$ in Eq.~\eqref{eq:GN_update} results in
\begin{equation}
\label{eq:temp_GN_eq}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H(\breve{\bd}-\breve{\bv}), 
\end{equation}
Substituting the first identity of Eq.~\eqref{eq:identities} into Eq.~\eqref{eq:temp_GN_eq} and simplifying the result 
\begin{equation}
\label{eq:one_thrid}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd}-\frac{1}{3}\breve{\bz}.
\end{equation}
It now trivially follows that:
\begin{equation}
\label{eq:two_thrids}
\breve{\bz}_{k+1} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd} + \frac{2}{3}\breve{\bz}_{k}. 
\end{equation}
Eq.~\eqref{eq:two_thrids} shows us that in the case of redundant calibration we can calculate the GN update step without calculating the residual. The 
normal skymodel-based equivalent of Eq.~\eqref{eq:two_thrids} is equal to \citep{Smirnov2015}:
\begin{equation}
\label{eq:one_half}
\breve{\bg}_{k+1} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd} + \frac{1}{2}\breve{\bg}_{k}, 
\end{equation}
where $\breve{\bg} = [\bg^T,\conj{\bg}^T]^T$

FIX TRANSPOSE PROBLEM

@@

On the odd iterations $\lambda$ is chosen to be zero, which corresponds to an $\alpha$ equal to one. On the even iteration $\lambda$ is chosen to be equal to one, which corresponds
to an $\alpha$ equal to a half. Note that, on the odd iteration the influence that the estimate of the parameters of the previous iteration has on the current estimate is scaled
by a half. Note the similarity between the last terms of Eq.~\eqref{eq:stef_alpha} and Eq.~\eqref{eq:one_half} when $\alpha$ is an half.

@@

Inspecting Eq.~\eqref{eq:red_H} reveals that in the case of redundant calibration the Hessian's diagonal entries are also more significant than its off-diagonal entries.
If we substitute $\bJ^H\bJ$ with $\widetilde{\bH}$ (by its diagonal approximation) and replace $\breve{\br}$ with $\breve{\bd} - \breve{\bv}$ in Eq.~\eqref{eq:GN_update} we obtain
\begin{equation}
\label{eq:appr_GN}
 \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H(\breve{\bd}-\breve{\bv})
\end{equation}
Utilizing the second identity in Eq.~\eqref{eq:identities} allows us to simplify Eq.~\eqref{eq:appr_GN} to
\begin{equation}
  \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}-\breve{\bz}.
\end{equation}
It now trivially follows that
\begin{equation}
 \breve{\bz}_{k+1} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}.
\end{equation}
We obtain a similar result if we repeat the above procedure, only in this case we use Eq.~\eqref{eq:LM_update} instead,
namely
\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k, \label{eq:alpha}  
\end{align}
where $\alpha = \frac{1}{1+\lambda}$. Moreover, $\lambda = \frac{1-\alpha}{\alpha}$. The analytic expression of $\bJ^H\breve{\bd}$ will be very similar to the analytic 
expression of $\bJ^H\breve{\br}$, the only difference being that in Eq.~\eqref{eq:ab} the letter $r$ would be replaced by a $d$. If we substitute the analytic expression
of $\bJ^H\breve{\bd}$ and $\widetilde{\bH}^{-1}$ (which is easily computed as the matrix is a diagonal matrix) into Eq.~\eqref{eq:alpha} we obtain the following two update rules:
\begin{equation}
\label{eq:g_update}
g_{i}^{k+1} = \alpha \frac{\sum_{j\neq i} g_j^k \widetilde{y}_{ij}^{~\!\!k} d_{ij}}{\sum_{j\neq i} |g_j^k|^2|y_{\zeta_{ij}}^k|^2} + (1-\alpha) g_i^k, 
\end{equation}
and
\begin{equation}
\label{eq:y_update}
y_{i}^{k+1} = \alpha \frac{\sum_{pq \in \mathcal{PQ}_i} \conj{g}_p^k g_q^k d_{pq}}{\sum_{pq \in \mathcal{PQ}_i}|g_p^k|^2|g_q^k|^2} + (1-\alpha) y_i^k. 
\end{equation}

The question now arises what value should we use for $\alpha$? Although an exact mathematical proof for the optimal choice of $\alpha$ still eludes us, it is still possible to
venture a clever guess by studying what the choice of $\alpha$ is in the case of StEFCal.

If we wish to scale $\breve{\bz}$ by two thirds in Eq.~\eqref{eq:alpha} we should choose $\alpha$ equal to a third, which corresponds to a $\lambda$ equal to two.

At this point there is no way of knowing if this is mere coincidence. DEF REWRITE THIS.

REWRTIE THIS IN A DIFFERENT WAY. START WITH CHENGULAR AND JUST MENTION THE LINK TO STEFCAL'S CHOICE OF ALPHA.

The update rules in Eq.~\eqref{eq:lambda} and Eq.~\eqref{eq:alpha} have been derived before, by Chengular... The approach they followed is discussed in the Appendix.

Interestingly enough, if we substitute $\alpha = 1$ into Eq.~\ref{eq:g_update} then it reduces to the skymodel-based StEFCal update rule. In Chengular they propose 
an $\alpha = 0.3$.

In an attempt to merge the terminology that has independently develop in the general calibration and redundant calibration literature and to emphasize the close
relationship between Stefcal and the approach derived by I will use the label Redunandat SteFCal (R-Stefcal) to refer to the NLS method proposed by ...

****\\

with $\alpha = \frac{1}{1+\lambda}$. Moreover $\lambda = \frac{1-\alpha}{\alpha}$. So in Marthi and Chengular (2014) they use an $\alpha$ of 0.3, which corresponds to an LM damping factor $\lambda$
of $2\frac{1}{3}$.

NB:: NEED TO ADD SNR PLOTS HERE
PLUS IMAGE OF HESSIAN FOR THE DISCUSSION

\subsection{Conjugate Gradient Method}
\label{sec:pcg}

\subsubsection{Spectral Condition Number}
kappa + itr plots
\begin{figure*}
\centering
\subfigure[$\kappa$]{\includegraphics[width=0.47\textwidth]{./kappa.pdf}\label{fig:kappa}}
% V_R_3.pdf: 585x441 pixel, 72dpi, 20.64x15.56 cm, bb=0 0 585 441
\subfigure[Iterations required before and after Preconditioning]{\includegraphics[width=0.47\textwidth]{./cg_itr.pdf}\label{fig:cg_itr}}
\caption{The graphs presented here were generated using the second experimental setup in Table~\ref{tab:ch_parm}. In the left panel we have plotted the spectral condition number $\kappa$ of the Hessian $\bH$, before (magenta and red curves) and after preconditioning (blue curve), at different SNR values as a function of the
number of antennas $N$ in the array. This plot shows us that we can drastically reduce the condition number of $\bH$ by preconditioning. Moreover, $\kappa$ is also
independent of the problem size (the number of antennas in the array). The fact that $\kappa$ is small and independent of problem size (effectively constant) implies that it simply drops out 
of Eq.~\eqref{eq:cg_bound}. The right hand panel confirms this result. In the right hand panel we have plotted the number of major iterations (line 6 of Algorithm \ref{algo:CG}) required by the conjugate 
gradient method to invert $\bH$, before (magenta and red curves) and after preconditioning (blue and green curves), at different SNR values as a function of the number of antennas $N$ in the array.  
The right hand panel therefore shows us that the number of major iterations needed by the preconditioned conjugate gradient method to invert $\bH$ is independent of the number of antennas in the array
and is much smaller than the dimension of $\bH$. 
\label{fig:kappa_itr}} 
\end{figure*}

\subsubsection{Sparsity}

% \begin{enumerate}
% \item $\boldsymbol{H}$: is a $(4N-2)\times(4N-2)$ or a $P \times P$ matrix. $N$ denotes the number of antennas and $P$ denotes the number of parameters. This matrix
% contains $6N^2 - 2N - 2$ non-zero entries. It contains $16N^2 - 16N + 4$ entries. We can construct this matrix with $4N^2 -  4N$ or $\frac{1}{4} P^2 -1$ elementary operations.
% \item $\boldsymbol{A}$: is a $(2N-1)\times(2N-1)$ matrix. This matrix has $N^2 + N - 1$ non-zero entries. We can construct this matrix with $2\frac{1}{2} (N^2 -  N)$ elementary operations.  
% \item $\boldsymbol{B}$: is a $(2N-1)\times(2N-1)$ matrix. This matrix has $2N^2 - 2N$ non-zero entries. We can construct this matrix with $1\frac{1}{2} (N^2 -  N)$ elementary operations.
% \item $\boldsymbol{C}$: is a $N\times N$ matrix. This matrix has $N$ non-zero entries. We can construct this matrix with $N^2-N$ elementary operations.
% \item $\boldsymbol{D}$: is a $N \times (N-1)$ matrix. This matrix has $\frac{1}{2} (N^2 -  N)$ non-zero entries. We can construct this matrix with $\frac{1}{2} (N^2 -  N)$ elementary operations. 
% \item $\boldsymbol{E}$: is a $(N-1) \times (N-1)$ matrix. This matrix has $(N-1)$ non-zero entries. We can construct this matrix with $\frac{1}{2} (N^2 -  N)$ elementary operations.  
% \item $\boldsymbol{F}$: is a $N \times N$ matrix. This matrix has $N^2 - N$ non-zero entries. We can construct this matrix with $\frac{1}{2} (N^2 -  N)$ elementary operations.
% \item $\boldsymbol{G}$: is a $N \times (N-1)$ matrix. This matrix has $\frac{1}{2} (N^2 -  N)$ non-zero entries. We can construct this matrix with $\frac{1}{2} (N^2 -  N)$ elementary operations.
% \item $\boldsymbol{0}$: is a $(N-1) \times (N-1)$ all zero matrix. 
% \end{enumerate}

>>>>

\newcommand{\bz}{\bmath{z}}
\newcommand{\bs}{\bmath{s}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\bB}{\bmath{B}}
\newcommand{\bC}{\bmath{C}}
\newcommand{\bE}{\bmath{E}}
\newcommand{\bF}{\bmath{F}}
\newcommand{\bG}{\bmath{G}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bH}{\bmath{H}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\bO}{\bmath{O}}
\newcommand{\bP}{\bmath{P}}
\newcommand{\bQ}{\bmath{Q}}
\newcommand{\bR}{\bmath{R}}
\newcommand{\bI}{\bmath{I}}
\newcommand{\ba}{\bmath{a}}
\newcommand{\bb}{\bmath{b}}
\newcommand{\bx}{\bmath{x}}
\newcommand{\bp}{\bmath{p}}
\newcommand{\bmJ}{\bmath{\mathcal{J}}}
\newcommand{\bmH}{\bmath{\mathcal{H}}}
\newcommand{\bzero}{\bmath{0}}
%\newcommand{\bvarrho}{\bmath{\varrho}}
%\newcommand{\bnu}{\bmath{\nu}}
%\newcommand{\bvarphi}{\bmath{\varphi}}
\newcommand{\conj}[1]{\overline{#1}}

@@

\section{Conjugate Gradient Method}
\label{sec:conj_grad}
The Conjugate Gradient (CG) method was independently discovered by \citet{Hestenes1973} and \citet{Stiefel1952}. They later published a joint paper, which is now considered as the seminal
reference on CG \citep{Hestenes1952}. The iterative CG method is used to solve a particular class of linear system. The CG method is generally used to solve
\begin{equation}
\label{eq:linear_system}
\bb = \bA\bx,
\end{equation}
where $\bb\in\mathbb{C}^P$ is a known complex column vector of size $P$, $\bx\in\mathbb{C}^P$ is an unknown complex column vector with the same length as $\bb$, and $\bA\in\mathbb{C}^{P\times P}$ is a square positive-definite Hermitian matrix with the appropriate dimensions.  
Moreover, using the CG method to solve Eq.~\eqref{eq:linear_system} will only be computationally advantageous if $\bA$ is also sparse (contain many zero entries).
Using the iterative CG method to solve large sparse linear sytems was popularized by \citet{Reid1971}. A good tutorial on the CG method can be found in \citep{Shewchuk1994}.
The iterative CG method is presented in Algorithm \ref{algo:CG}.

@@

\subsection{Normal Equation}
\label{sec:normal}
Lets assume that instead of Eq.~\eqref{eq:linear_system} we have a more general linear system, i.e.
\begin{equation}
 \bb = \bB\bx,
\end{equation}
where $\bb\in\mathbb{C}^K$, $\bx\in\mathbb{C}^P$  and $\bB\in\mathbb{C}^{K \times P}$, with $K > P$. We can use the normal equation 
\begin{equation}
\label{eq:normal_equation}
\bB^H\bB\bx = \bB^H\bb 
\end{equation}
to estimate the $\bx$ that minimizes
\begin{equation}
\label{eq:norm_ls}
\|\bb-\bB\bx\|_F^2. 
\end{equation}
There are a few important observations that we can make while inspecting Eq.~\eqref{eq:normal_equation}:
\begin{enumerate}
\item $\bB^H\bB$ is a square positive semi-definite Hermitian matrix by construction.
\item $\bB^H\bb$ is in the column range of $\bB^H\bB$; this follows trivially from 
\begin{equation}
\bB^H\bb \in \mathcal{R}(\bB^H) \implies \bB^H\bb \in \mathcal{R}(\bB^H\bB).   
\end{equation}
\end{enumerate}

@@

\subsubsection{Complex GN and LM}
In this section we discuss how we can use the GN and LM algorithms to solve Eq.~\eqref{eq:least_squares_complex} (i.e. estimate $\breve{\bz}$). The complex Jacobian is defined to be
\begin{equation}
\label{eq:Jacobian}
\bJ = \begin{bmatrix}
       \bmJ & \bmJ^*\\
       \conj{\bmJ}^* & \conj{\bmJ} 
      \end{bmatrix},
\end{equation}
where 
\begin{align}
\bmJ &= \frac{\partial \bv}{\partial \bz}, & \bmJ^* &= \frac{\partial \bv}{\partial \conj{\bz}}. 
\end{align}
In Eq.~\eqref{eq:Jacobian}, $\frac{\partial}{\partial \bz}$ and $\frac{\partial}{\partial \conj{\bz}}$ respectively denote the cogradient operator and the conjugate cogradient operator \citep{Sorber2012}.
The GN update step is now defined as:
\begin{equation}
\label{eq:GN_update}
 \Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\br}.
\end{equation}
The LM update rule is very similar, the major difference being a damping factor $\lambda$ is introduced:
\begin{equation}
\label{eq:LM_update}
\Delta \breve{\bz} = (\bJ^H\bJ + \lambda\bD)^{-1}\bJ^H\breve{\br},
\end{equation}
where $\bD=\bI\odot\bJ^H\bJ$. We refer to $\bJ^H\bJ$ as the Hessian matrix $\bH$ and to $\bJ^H\bJ + \lambda\bD$ as the modified Hessian matrix $\bmH$.

@@

Replacing $\breve{\br}$ with $\breve{\bd}-\breve{\bv}$ in Eq.~\eqref{eq:GN_update} results in
\begin{equation}
\label{eq:temp_GN_eq}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H(\breve{\bd}-\breve{\bv}), 
\end{equation}
Substituting the first identity of Eq.~\eqref{eq:identities} into Eq.~\eqref{eq:temp_GN_eq} and simplifying the result 
\begin{equation}
\label{eq:one_thrid}
\Delta \breve{\bz} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd}-\frac{1}{3}\breve{\bz}.
\end{equation}
It now trivially follows that:
\begin{equation}
\label{eq:two_thrids}
\breve{\bz}_{k+1} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd} + \frac{2}{3}\breve{\bz}_{k}. 
\end{equation}
Eq.~\eqref{eq:two_thrids} shows us that in the case of redundant calibration we can calculate the GN update step without calculating the residual. 
% The 
% normal skymodel-based equivalent of Eq.~\eqref{eq:two_thrids} is equal to \citep{Smirnov2015}:
% \begin{equation}
% \label{eq:one_half}
% \breve{\bg}_{k+1} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd} + \frac{1}{2}\breve{\bg}_{k}, 
% \end{equation}
% where $\breve{\bg} = [\bg^T,\conj{\bg}^T]^T$
% 
% FIX TRANSPOSE PROBLEM

@@

On the odd iterations $\lambda$ is chosen to be zero, which corresponds to an $\alpha$ equal to one. On the even iteration $\lambda$ is chosen to be equal to one, which corresponds
to an $\alpha$ equal to a half. Note that, on the odd iteration the influence that the estimate of the parameters of the previous iteration has on the current estimate is scaled
by a half. Note the similarity between the last terms of Eq.~\eqref{eq:stef_alpha} and Eq.~\eqref{eq:one_half} when $\alpha$ is a half.

@@

Inspecting Eq.~\eqref{eq:red_H} reveals that in the case of redundant calibration the Hessian's diagonal entries are also more significant than its off-diagonal entries.
If we substitute $\bJ^H\bJ$ with $\widetilde{\bH}$ (by its diagonal approximation) and replace $\breve{\br}$ with $\breve{\bd} - \breve{\bv}$ in Eq.~\eqref{eq:GN_update} we obtain
\begin{equation}
\label{eq:appr_GN}
 \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H(\breve{\bd}-\breve{\bv})
\end{equation}
Utilizing the second identity in Eq.~\eqref{eq:identities} allows us to simplify Eq.~\eqref{eq:appr_GN} to
\begin{equation}
  \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}-\breve{\bz}.
\end{equation}
It now trivially follows that
\begin{equation}
 \breve{\bz}_{k+1} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}.
\end{equation}
We obtain a similar result if we repeat the above procedure, only in this case we use Eq.~\eqref{eq:LM_update} instead,
namely
\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k. \label{eq:alpha}  
\end{align}
The analytic expression of $\bJ^H\breve{\bd}$ will be very similar to the analytic 
expression of $\bJ^H\breve{\br}$, the only difference being that in Eq.~\eqref{eq:ab} the letter $r$ would be replaced by a $d$. If we substitute the analytic expression
of $\bJ^H\breve{\bd}$ and $\widetilde{\bH}^{-1}$ (which is easily computed as the matrix is a diagonal matrix) into Eq.~\eqref{eq:alpha} we obtain the following two update rules:
\begin{equation}
\label{eq:g_update}
g_{i}^{k+1} = \alpha \frac{\sum_{j\neq i} g_j^k \widetilde{y}_{ij}^{~\!\!k} d_{ij}}{\sum_{j\neq i} |g_j^k|^2|y_{\zeta_{ij}}^k|^2} + (1-\alpha) g_i^k, 
\end{equation}
and
\begin{equation}
\label{eq:y_update}
y_{i}^{k+1} = \alpha \frac{\sum_{pq \in \mathcal{PQ}_i} \conj{g}_p^k g_q^k d_{pq}}{\sum_{pq \in \mathcal{PQ}_i}|g_p^k|^2|g_q^k|^2} + (1-\alpha) y_i^k. 
\end{equation}
The computational complexity of inverting $\widetilde{\bH}$ is $\mathbb{O}(P)$.

Eq.~\eqref{eq:g_update} and Eq.~\eqref{eq:y_update} are the exact same iterative new parameter estimators derived by \citet{Marthi2014}. Als note that Eq.~\eqref{eq:g_update} is the fundamental
iterative StEfCal new parameter estimator. We have therefore successfully used the diagonal approximation approach suggested by \citet{Smirnov2015} to re-derive the ADI method presented in 
\citet{Marthi2014} and in doing so we have shown that the algorithm in \citet{Marthi2014} is actually redundant StEfCal. We could also have shown this by using a similar approach 
to the one presented in \citet{Salvini2014}.

The question now arises what value should we use for $\alpha$? In \citet{Marthi2014} they propose 
$\alpha = 0.3$. Although an exact mathematical proof for the optimal choice of $\alpha$ still eludes us, it is still possible to
venture a clever guess by studying what the choice of $\alpha$ is in the case of skymodel-based StEFCal. Recall from Section~\ref{sec:sbc} that $\alpha$ is equal to a half 
in the case of StEFCal. If we wish to mimic this behaviour for the redundant calibration use case we need to scale $\breve{\bz}$ by two thirds in Eq.~\eqref{eq:alpha} (see Eq.~\eqref{eq:two_thrids}) which implies that we should choose $\alpha$ equal to a third, which corresponds to a $\lambda$ equal to two,
which is the value we used in this paper.

% At this point there is no way of knowing if this is mere coincidence. DEF REWRITE THIS.
% 
% REWRTIE THIS IN A DIFFERENT WAY. START WITH CHENGULAR AND JUST MENTION THE LINK TO STEFCAL'S CHOICE OF ALPHA.
% 
% The update rules in Eq.~\eqref{eq:lambda} and Eq.~\eqref{eq:alpha} have been derived before, by Chengular... The approach they followed is discussed in the Appendix.
% 
% Interestingly enough, if we substitute $\alpha = 1$ into Eq.~\ref{eq:g_update} then it reduces to the skymodel-based StEFCal update rule. In Chengular they propose 
% an $\alpha = 0.3$.
% 
% In an attempt to merge the terminology that has independently develop in the general calibration and redundant calibration literature and to emphasize the close
% relationship between Stefcal and the approach derived by I will use the label Redunandat SteFCal (R-Stefcal) to refer to the NLS method proposed by ... 
% 
% ****\\
% 
% with $\alpha = \frac{1}{1+\lambda}$. Moreover $\lambda = \frac{1-\alpha}{\alpha}$. So in Marthi and Chengular (2014) they use an $\alpha$ of 0.3, which corresponds to an LM damping factor $\lambda$
% of $2\frac{1}{3}$.
% 
% NB:: NEED TO ADD SNR PLOTS HERE
% PLUS IMAGE OF HESSIAN FOR THE DISCUSSION

\subsection{Preconditioned Conjugate Gradient Method}
\label{sec:pcg}
In this section we investigate the computational complexity of the PCG method when applied to the redundant calibration problem. 
The PCG method was presented in Section~\ref{sec:conj_grad}.
The PCG method differs from the ADI method presented in Section~\ref{sec:adi} in that in the case of PCG we compute the exact inverse of the modified Hessian instead 
of using some sort of approximation as is the case for ADI. As we mentioned in Section~\ref{sec:pcg} there
are two factors which influence the computational complexity of the PCG method, namely the spectral condition number and the sparsity of the matrix we wish to invert. 
We used a $\lambda$ value of two, implying we used Eq.~\eqref{eq:LM_update} instead of Eq.~\eqref{eq:GN_update} throughout this section.
We respectively discuss the spectral condition number and the sparsity of the modified Hessian, which is a non-singular matrix in Section~\ref{sec:scn} and Section~\ref{sec:sparsity}.
It is interesting to note, that the Hessian itself is singular which means that if we are to use Eq.~\eqref{eq:GN_update} instead we would need to be able invert a singular matrix. In Section~\ref{sec:normal},
we showed that the PCG method can in fact be used to invert a singular Hessian matrix.

\subsubsection{Spectral Condition Number}
\label{sec:scn}
kappa + itr plots
\begin{figure*}
\centering
\subfigure[$\kappa$]{\includegraphics[width=0.47\textwidth]{./kappa.pdf}\label{fig:kappa}}
% V_R_3.pdf: 585x441 pixel, 72dpi, 20.64x15.56 cm, bb=0 0 585 441
\subfigure[Iterations required before and after Preconditioning]{\includegraphics[width=0.47\textwidth]{./cg_itr.pdf}\label{fig:cg_itr}}
\caption{The graphs presented here were generated using the second experimental setup in Table~\ref{tab:ch_parm}. In the left panel we have plotted the spectral condition number $\kappa$ of the modified Hessian $\bH$, before (magenta and red curves) and after preconditioning (blue curve), at different SNR values as a function of the
number of antennas $N$ in the array. This plot shows us that we can drastically reduce the condition number of $\bH$ by preconditioning. Moreover, $\kappa$ is also
independent of the problem size (the number of antennas in the array). The fact that $\kappa$ is small and independent of problem size (effectively constant) implies that it simply drops out 
of Eq.~\eqref{eq:cg_bound}. The right hand panel confirms this result. In the right hand panel we have plotted the number of major iterations (line 6 of Algorithm \ref{algo:CG}) required by the conjugate 
gradient method to invert $\bH$, before (magenta and red curves) and after preconditioning (blue and green curves), at different SNR values as a function of the number of antennas $N$ in the array.  
The right hand panel therefore shows us that the number of major iterations needed by the preconditioned conjugate gradient method to invert $\bH$ is independent of the number of antennas in the array
and is much smaller than the dimension of $\bH$. 
\label{fig:kappa_itr}} 
\end{figure*}

\subsubsection{Sparsity}
\label{sec:sparsity}
% \begin{enumerate}
% \item $\boldsymbol{H}$: is a $(4N-2)\times(4N-2)$ or a $P \times P$ matrix. $N$ denotes the number of antennas and $P$ denotes the number of parameters. This matrix
% contains $6N^2 - 2N - 2$ non-zero entries. It contains $16N^2 - 16N + 4$ entries. We can construct this matrix with $4N^2 -  4N$ or $\frac{1}{4} P^2 -1$ elementary operations.
% \item $\boldsymbol{A}$: is a $(2N-1)\times(2N-1)$ matrix. This matrix has $N^2 + N - 1$ non-zero entries. We can construct this matrix with $2\frac{1}{2} (N^2 -  N)$ elementary operations.  
% \item $\boldsymbol{B}$: is a $(2N-1)\times(2N-1)$ matrix. This matrix has $2N^2 - 2N$ non-zero entries. We can construct this matrix with $1\frac{1}{2} (N^2 -  N)$ elementary operations.
% \item $\boldsymbol{C}$: is a $N\times N$ matrix. This matrix has $N$ non-zero entries. We can construct this matrix with $N^2-N$ elementary operations.
% \item $\boldsymbol{D}$: is a $N \times (N-1)$ matrix. This matrix has $\frac{1}{2} (N^2 -  N)$ non-zero entries. We can construct this matrix with $\frac{1}{2} (N^2 -  N)$ elementary operations. 
% \item $\boldsymbol{E}$: is a $(N-1) \times (N-1)$ matrix. This matrix has $(N-1)$ non-zero entries. We can construct this matrix with $\frac{1}{2} (N^2 -  N)$ elementary operations.  
% \item $\boldsymbol{F}$: is a $N \times N$ matrix. This matrix has $N^2 - N$ non-zero entries. We can construct this matrix with $\frac{1}{2} (N^2 -  N)$ elementary operations.
% \item $\boldsymbol{G}$: is a $N \times (N-1)$ matrix. This matrix has $\frac{1}{2} (N^2 -  N)$ non-zero entries. We can construct this matrix with $\frac{1}{2} (N^2 -  N)$ elementary operations.
% \item $\boldsymbol{0}$: is a $(N-1) \times (N-1)$ all zero matrix. 
% \end{enumerate}
